---
title: "Introduction to rcadastre"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to rcadastre}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rcadastre)
```

# Overview

The rcadastre package provides tools to download, prepare, and use French cadastral datasets.
It integrates data from various official sources (Etalab, PCI, CDG, etc.) and offers helpers for reading, configuring, and working with administrative boundaries.
An interactive Shiny app is also included for users who prefer a graphical interface.

# Installation

```{r installation, eval = FALSE}
# From CRAN (once published)
install.packages("rcadastre")

# Development version from GitHub
devtools::install_github("mucau/rcadastre")
```

# Main features

The package covers several workflows:

Etalab data: download and read datasets provided by Etalab
(`get_etalab_data()`, `get_etalab_bundle()`).

PCI data: access and manage cadastral PCI data
(`get_pci_data()`).

Administrative boundaries: included datasets for `commune_2025`, `departement_2025`, and `region_2025`.

## Example workflow

```{r main_example, eval = FALSE}
library(rcadastre)

# Load example dataset
data(commune_2025)

# Inspect
head(commune_2025)

# Download Etalab data
etalab <- get_etalab_data(insee_code = "72187") # 'Marigné-Laillé' for example

# Work with PCI data
pci <- get_pci_data(insee_code = "72187", format = "dxf")  # 'Marigné-Laillé' for example

```

# Other features
CDG (cadastre.data.gouv) utilities: detect, construct, and download CDG datasets urls
(`cdg_detect_millesimes()`, `cdg_download_archives()`, etc.).

Configuration utilities: manage paths and metadata
(`cfg_load()`, `cfg_get_data()`).

# Shiny application

An interactive Shiny app is bundled within the package. You can launch it with:

```{r app, eval = FALSE}
rcadastre::launch_app()
```

This provides a user-friendly interface for exploring cadastral data.

# Conclusion

The rcadastre package is designed to facilitate reproducible and transparent access to French cadastral datasets, either programmatically through R functions or interactively via the Shiny application.

Future developments will include extended support for new data sources and more utilities for spatial data management.
